A Fast Unified Model for Parsing and Sentence Understanding

### 2016-05-27 writing/hard_stack_paper/paper.tex
Incremental paper update. Off to lunch.

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here
%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

@@

     \author{}
%    \author{
%    Samuel R.\ Bowman$^{1,2,5,}$\thanks{~\,The first two authors contributed equally.} \\
%    \texttt{\small sbowman@stanford.edu} \\
%    \And
%    Jon Gauthier$^{2,3,5,*}$ \\
%    \texttt{\small jgauthie@stanford.edu} \\
%    \And
%    Abhinav Rastogi$^{4,5}$ \\
%    \texttt{\small arastogi@stanford.edu} \\
%    \AND
%    Raghav Gupta$^{6}$ \\
%    \texttt{\small rgupta93@stanford.edu} \\
%    \And
%    Christopher D.\ Manning$^{1,2,5,6}$\\
%    \texttt{\small manning@stanford.edu}\\
%    \And
%    Christopher Potts$^{1}$\\
%    \texttt{\small cgpotts@stanford.edu}
%    \AND\\[-3ex]
%    {$^{1}$Stanford Linguistics\quad
%    $^{2}$Stanford NLP Group\quad
%    $^{3}$Stanford Symbolic Systems}\\
%    {$^{4}$Stanford Electrical Engineering\quad
%    $^{5}$Stanford AI Lab\quad
%    $^{6}$Stanford Computer Science}
%    }

@@

We evaluate SPINN on the Stanford Natural Language Inference entailment task \citep[SNLI,][]{snli:emnlp2015}, and find that it significantly outperforms other sentence-encoding-based models, and that it yields speed increases of up to 25$\times$ over a standard TreeRNN implementation.

@@

For SPINN to operate on unparsed inputs, it needs to produce its own transition sequence $\mathbf t$ rather than relying on an external parser to supply it as part of the input. To do this, the model predicts $t_t$ at each step using a simple two-way softmax classifier whose input is the state of the tracking LSTM:
\begin{equation}
\vec{p}_{\text{t}} = \text{softmax}(W_{\text{trans}}\vec{h}_{\text{tracking}} + \vec{b}_{\text{trans}})
\end{equation}
At test time, the model uses whichever transition (i.e., \shift\ or \reduce) is assigned a higher probability. The prediction function is trained to mimic the decisions of an external parser. These decisions are used as the inputs to the model during training. For SNLI, we use the binary Stanford PCFG Parser parses that are included with the corpus. We did not find scheduled sampling \citep{bengio2015scheduled}---having the model use its own transition decisions sometimes at training time---to help.

@@

\snli
{A \textit{woman} in red blouse is \textit{standing} with small blond \textit{child} in front of a small folding chalkboard.}
{a \textit{woman} \textit{stands} with her \textit{child}}
{neutral}

>>>>

\aclfinalcopy % Uncomment this line for the final submission
\def\aclpaperid{265} %  Enter the acl Paper ID here
%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

@@

\author{
Samuel R.\ Bowman$^{1,2,5,}$\thanks{~\,The first two authors contributed equally.} \\
\texttt{\small sbowman@stanford.edu} \\
\And
Jon Gauthier$^{2,3,5,*}$ \\
\texttt{\small jgauthie@stanford.edu} \\
\And
Abhinav Rastogi$^{4,5}$ \\
\texttt{\small arastogi@stanford.edu} \\
\AND
Raghav Gupta$^{6}$ \\
\texttt{\small rgupta93@stanford.edu} \\
\And
Christopher D.\ Manning$^{1,2,5,6}$\\
\texttt{\small manning@stanford.edu}\\
\And
Christopher Potts$^{1}$\\
\texttt{\small cgpotts@stanford.edu}
\AND\\[-3ex]
{$^{1}$Stanford Linguistics\quad
$^{2}$Stanford NLP Group\quad
$^{3}$Stanford Symbolic Systems}\\
{$^{4}$Stanford Electrical Engineering\quad
$^{5}$Stanford AI Lab\quad
$^{6}$Stanford Computer Science}
}

@@

We evaluate SPINN on the Stanford Natural Language Inference entailment task \citep[SNLI,][]{snli:emnlp2015}, and find that it significantly outperforms other sentence-encoding-based models, even with a relatively simple and underpowered implementation of the built-in parser. We also find that SPINN yields speed increases of up to 25$\times$ over a standard TreeRNN implementation.

@@

For SPINN to operate on unparsed inputs, it needs to produce its own transition sequence $\mathbf a$ rather than relying on an external parser to supply it as part of the input. To do this, the model predicts $a_t$ at each step using a simple two-way softmax classifier whose input is the state of the tracking LSTM:
\begin{equation}
\vec{p}_{\text{a}} = \text{softmax}(W_{\text{trans}}\vec{h}_{\text{tracking}} + \vec{b}_{\text{trans}})
\end{equation}
Note that this is the close to being simplest viable implementation of a transition decision function. In contrast, the decision functions in sate-of-the-art transition-based parsers tend to use significantly richer feature sets as inputs, including features containing information about several upcoming words on the buffer instead of just one. We use this simple parser here, and leave a more thorough investigation of this component of the model to future work.

At test time, the model uses whichever transition (i.e., \shift\ or \reduce) is assigned a higher (unnormalized) probability. The prediction function is trained to mimic the decisions of an external parser. These decisions are used as the inputs to the model during training. For SNLI, we use the binary Stanford PCFG Parser parses that are included with the corpus. We did not find scheduled sampling \citep{bengio2015scheduled}---having the model use its own transition decisions sometimes at training time---to help.

@@

\snli
{A \textit{woman} in red blouse is \textit{standing} with small blond \textit{child} in front of a small folding chalkboard.}
{a \textit{woman} \textit{stands} with her \textit{child}}
{neutral}
The three SPINN models appear to be 
\todo{Replace above with example of negation, and stats}

\todo{Replace bewol with comment/example about very long sentences exaggerating difference.}
